Nested Stochastic Block Models Applied to the Analysis of Single Cell Data

### 2021-04-27 supplementary.tex
Final retouch

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Tian_NSBM0.png}
\caption[]{Analysis of a mixture of 5 known cell lines. (A) UMAP  embedding of cell lines from the sc-mixology experiment colored by the level 0 of the hierarchy proposed by the nested Stochastic Block Model (B) UMAP embedding colored by the classification made by SCCAF when partitions in (A) are used.}\label{Tian_NSBM0}
\end{figure}
\clearpage
%\begin{figure}[htbp]
%\centering
%\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_S2.png}
%\caption[]{Adjusted Rand Index for different \emph{k}NN graphs after MCMC run. Maximal ARI over all hierarchy level is shown. Darker color indicates higher concordance with the ground truth}\label{MPFigure:9060BBC5-898E-4AA7-A57D-D221167F7250}
%\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Hemato_Supp.png}
\caption[]{Analysis of hematopoietic differentiation. (A) Low dimensional embedding of single cells colored by original cell type and pseudotime. (B) Cells are colored according to the nSBM grouping at level 3 of the hierarchy, next to a radial tree representation of the same model.}\label{Figure_Hemato_Supp}
\end{figure}
\clearpage

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Paul15_Leiden_r.png}
\caption[]{Low dimension embedding of single cells for hematopoietic differentiation colored according to Leiden clustering at decreasing resolution, from 1.0 to 0.1. Lowering the distribution does not grant that cells are grouped in a hierarchical way, \emph{e.g.} groups 6 and 8 in the Erythroid branch at resolution $\gamma=1$ are merged or split at coarser resolutions ($\gamma=0.6$ and $\gamma=0.3$).}\label{Figure_Paul15_Leiden_r}
\end{figure}
\clearpage

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,width=0.50\textheight]{Figure_Stability.png}
\caption[]{Cell Stability. UMAP embeddings of PBMC data profiled with four different technologies ranked by their quality. Cells are colored by the Cell Stability metric.}\label{Figure_Stability}
\end{figure}
\clearpage

@@

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=1\textheight]{FigureOptimalLevel.png}
\caption[]{Choice of the optimal hierarchy level. Datasets analyzed for choice of the most relevant hierarchy level are represented here, from top to bottom in the same order as in Table \ref{table_optimal}. For each dataset we report the UMAP embedding coloured by the annotation given in the corresponding manuscript, the profile of modularity $Q$ at different level of the hierarchy and the UMAP embeddings coloured by the level according to $i^k$ or $i^Q$. The dashed line in modularity plots represents the modularity calculated using the annotation from the corresponding manuscripts.}\label{FigureOptimalLevel}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Tian_NSBM0.png}
\caption[]{Analysis of a mixture of 5 known cell lines. (A) UMAP  embedding of cell lines from the sc-mixology experiment coloured by the level 0 of the hierarchy proposed by the nested Stochastic Block Model (B) UMAP embedding coloured by the classification made by SCCAF when partitions in (A) are used.}\label{Tian_NSBM0}
\end{figure}
\clearpage
%\begin{figure}[htbp]
%\centering
%\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_S2.png}
%\caption[]{Adjusted Rand Index for different \emph{k}NN graphs after MCMC run. Maximal ARI over all hierarchy level is shown. Darker color indicates higher concordance with the ground truth}\label{MPFigure:9060BBC5-898E-4AA7-A57D-D221167F7250}
%\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Hemato_Supp.png}
\caption[]{Analysis of hematopoietic differentiation. (A) Low dimensional embedding of single cells coloured by original cell type and pseudotime. (B) Cells are coloured according to the nSBM grouping at level 3 of the hierarchy, next to a radial tree representation of the same model.}\label{Figure_Hemato_Supp}
\end{figure}
\clearpage

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=0.75\textheight]{Figure_Paul15_Leiden_r.png}
\caption[]{Low dimension embedding of single cells for hematopoietic differentiation coloured according to Leiden clustering at decreasing resolution, from 1.0 to 0.1. Lowering the distribution does not grant that cells are grouped in a hierarchical way, \emph{e.g.} groups 6 and 8 in the Erythroid branch at resolution $\gamma=1$ are merged or split at coarser resolutions ($\gamma=0.6$ and $\gamma=0.3$).}\label{Figure_Paul15_Leiden_r}
\end{figure}
\clearpage

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,width=0.50\textheight]{Figure_Stability.png}
\caption[]{Cell Stability. UMAP embeddings of PBMC data profiled with four different technologies ranked by their quality. Cells are coloured by the Cell Stability metric.}\label{Figure_Stability}
\end{figure}
\clearpage

@@

\begin{figure}[htbp]
\centering
\includegraphics[keepaspectratio,width=\textwidth,height=1\textheight]{FigureOptimalLevel.png}
\caption[]{Choice of the optimal hierarchy level. Datasets analysed for choice of the most relevant hierarchy level are represented here, from top to bottom in the same order as in Table \ref{table_optimal}. For each dataset we report the UMAP embedding coloured by the annotation given in the corresponding manuscript, the profile of modularity $Q$ at different level of the hierarchy and the UMAP embeddings coloured by the level according to $i^k$ or $i^Q$. The dashed line in modularity plots represents the modularity calculated using the annotation from the corresponding manuscripts.}\label{FigureOptimalLevel}
\end{figure}
